Mirror, mirror on the wall. Who's the best match of them all?

### 2023-11-22 PNAS/index.Rnw

This issue has been raised in the past with regard to DNA \citep{thompson2003} and fingerprints \citep{koehler2021}: one of the issues \citep{fine2006} leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid bombing case was that the large size of the IAFIS database used to locate similar prints made it possible to locate `unusually' similar non-matches.
%
\hh{In this paper, we discuss that very close non-matches are far from an unusual phenomenon  but a direct consequence of a large number of comparisons, and simply reflect the power of the search algorithms.}
%
\hh{In order to avoid embarassing false accusation and a further erosion of the public's trust in science, we need to address the problem of multiple comparisons by controlling their effect on false discovery rates.}
%
\hh{Database searches are an example where the number of searches is explicitly available as the number of objects meeting the search criteria. }

>>>>

This issue has been raised in the past with regard to DNA \citep{thompson2003} and fingerprints \citep{koehlerFingerprintErrorRate2021}: one of the issues \citep{fine2006} leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid bombing case was that the large size of the IAFIS database used to locate similar prints made it possible to locate `unusually' similar non-matches.
\svp{Very close non-matches are a direct consequence of a large number of comparisons; they will occur more frequently as databases increase in size and algorithms become more powerful.}
% In this paper, we discuss that very close non-matches are far from an unusual phenomenon  but a direct consequence of a large number of comparisons, and simply reflect the power of the search algorithms.

In order to avoid embarassing false accusations and a further erosion of the public's trust in science, we need to address the problem of multiple comparisons by controlling their effect on false discovery rates.
%
% \hh{Database searches are an example where the number of searches is explicitly available as the number of objects meeting the search criteria. } % This doesn't seem super-relevant and distracts from the continuity between the algorithm discussion above and the next paragraph
